Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-09 ApproximateCode.tex
Update ApproximateCode.tex
grammar mistake

Considering the vital role the I frame plays in the video coding, we therefore define I frame data as the critical data of a video file. Although some part of P frames may play a relatively important role in the decoding process of a video, it’s importance can not exceed that of the I frames.

>>>>

Considering the vital role the I frame plays in the video coding, we therefore define I frame data as the critical data of a video file. Although some part of P frames may play a relatively important role in the decoding process of a video, its importance can not exceed that of the I frames.
